### 2023-01-10 definitions.tex
Harmonizing notations Pred Pre & pre

\begin{definition}{ (index)}. 
If $S$ is a WSTS with strong monotony and $I \subseteq S$  is an upward-closed set and $k \geq 0$, let $I^k= \bigcup_{0 \leq j \leq k} pre^j(I)$.
The {\em index} $k(I)$ is the
smallest $k_0$ s.t. $I^k = I^{k_0}$ for all $k \geq k_0$.
\end{definition}

@@

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup pre(I^k ) = I \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$$
\alain{n'est-ce pas $I^{k+1} = I^k \cup pre(I^k ) = I^k \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$ ?}

Since $pre(\uparrow \{s' \}$) is computable for any $s'\in S$ by definition, we obtain a finite generating set of $I^{k+1}$ . By
Fact~\ref{fact basis}, we can compute a basis of $I^{k+1}$.
\end{proof}
\subsection{Defining resilience}

@@

\alain{cette dernière propriété fait penser à la $t$-liveness dans un rdPetri ou n'importe quel modèle monotone..qui peut s'exprimer par $ ~ \forall s' \in S ~ (s \rightarrow^* s') \implies \exists s'' \in U_t ~ s' \rightarrow^{*} s''$ ? avec $U_t=\uparrow Pre(t)$=la clôture par le haut des préconditions pour déclencher la transition $t$}
\end{proof}

@@

\begin{proof}
From Fact~\ref{stop condition}, there exists $k \in \N$ such that
$pre^*(I) = I^{k_m}$. We can compute this $k_m$ by iteratively computing
$I^{k+1}$ from $I^k$, checking $I^{k+1}=I^k$, 
returning $k_m$ if that is the case.
Then, because $k_m$-resilience is decidable, 
checking $\uparrow post^*(s) \cap J \subseteq I^k = pre^*(I)$ is,
and resilience is decidable.
% \textcolor{red}{à faire Mathieu}
\end{proof}

>>>>

\begin{definition}{ (index)}. 
If $S$ is a WSTS with strong monotony and $I \subseteq S$  is an upward-closed set and $k \geq 0$, let $I^k= \bigcup_{0 \leq j \leq k} \pred^j(I)$.
The {\em index} $k(I)$ is the
smallest $k_0$ s.t. $I^k = I^{k_0}$ for all $k \geq k_0$.
\end{definition}

@@

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup \pred(I^k ) = I \cup
\bigcup_{s' \in B}
\pred(\uparrow \{s' \}).$$
\alain{n'est-ce pas $I^{k+1} = I^k \cup \pred(I^k ) = I^k \cup
\bigcup_{s' \in B}
\pred(\uparrow \{s' \}).$ ?}

Since $\pred(\uparrow \{s' \}$) is computable for any $s'\in S$ by definition, we obtain a finite generating set of $I^{k+1}$ . By
Fact~\ref{fact basis}, we can compute a basis of $I^{k+1}$.
\end{proof}
\subsection{Defining resilience}

@@

\alain{cette dernière propriété fait penser à la $t$-liveness dans un rdPetri ou n'importe quel modèle monotone..qui peut s'exprimer par $ ~ \forall s' \in S ~ (s \rightarrow^* s') \implies \exists s'' \in U_t ~ s' \rightarrow^{*} s''$ ? avec $U_t=\uparrow \pred(t)$=la clôture par le haut des préconditions pour déclencher la transition $t$}
\end{proof}

@@

\begin{proof}
From Fact~\ref{stop condition}, there exists $k \in \N$ such that
$\pred^*(I) = I^{k_m}$. We can compute this $k_m$ by iteratively computing
$I^{k+1}$ from $I^k$, checking $I^{k+1}=I^k$, 
returning $k_m$ if that is the case.
Then, because $k_m$-resilience is decidable, 
checking $\uparrow post^*(s) \cap J \subseteq I^k = \pred^*(I)$ is,
and resilience is decidable.
% \textcolor{red}{à faire Mathieu}
\end{proof}
